Robustly decorrelating errors with mixed quantum gates

### 2019-05-22 decorrelation/mixed_unitaries.tex
bibliography, cleaning up, and the like

\begin{abstract}
\noindent Coherent errors in quantum operations are ubiquitous. Whether arising from spurious environmental couplings or errors in control fields, such errors can accumulate rapidly and degrade the performance of a quantum circuit significantly more than an average gate fidelity may indicate. As Hastings \cite{Hastings2017} and Campbell \cite{Campbell2017} have recently shown, randomly sampling an ensemble of implementations of a target gate yields an effective quantum channel that well-approximates the target, but with dramatically suppressed coherent error. Our work begins by reformulating the results of Hastings and Campbell as a quantum optimal control problem. We then discuss a family of convex programs designed to improve the performance, implementability, and robustness of the resulting mixed quantum gates. Finally, we implement these mixed quantum gate on a superconducting qubit and discuss randomized benchmarking results consistent with a marked reduction in the coherent error.\\
{[1]} M. B. Hastings, \emph{Quantum Information \& Computation} 17, 488 (2017). \\
{[2]} E. Campbell, \emph{Physical Review A} 95, 042306 (2017).
\end{abstract}

@@

% ==============================================================================
% Section: Introduction
% ==============================================================================
\section{Introduction}
\label{sec:introduction}
\noindent The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIPs). Gate fidelities are now routinely in the 99\% to 99.99\% range \cite{Barends2014, Ballance2016, 1901.08035}, and dozens of individually-addressable qubits are becoming available on integrated devices. While these advances are promising steps forward on the path towards a computationally useful QIP, the quantum supremacy \cite{1203.5813} milestone has yet to be definitively reached. A critical limiting factor, of course, is errors in the quantum gate operations. \note{I think we can just strike this whole paragraph. I hate these introductions.}

The ultimate impact of a gate error on a quantum circuit depends strongly on both the magnitude and the nature of the error. Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or approximate gate compilations that induce repeatable, undesired unitary errors on the state of a QIP. Errors of this type are correlated in time may add up constructively or destructively, depending on the circuit. They are are  computationally expensive to model and, because coherent errors may amplify when gates are repeated, it can be difficult to place tight analytic bounds on circuit performance \cite{Beale2018}. Contrast this against random, or \emph{stochastic}, errors, which often result from high-frequency noise in the controls or the environment. Systems with stochastic errors can usually be accurately modeled by defining a rate of various discrete errors in the system, such as a bit flips or phase flips. These errors are significantly easier to simulate on a classical computer, and their impact on quantum circuits is much easier to estimate \cite{Beale2018}.

@@

Recent works by Campbell \cite{Campbell2017,1811.08017} and Hastings \cite{Hastings2017} have shown that coherent noise can be strongly suppressed by probabilistically mixing several distinct implementations of the target quantum gates. They focus on errors arising from various gate compilations, such as the Solovey-Kitaev algorithm, for which any lingering approximation errors are generally coherent, even if the native gates are perfect. Different approximate gate compilations of the same target unitary will almost certainly result in a different unitary error. So by selecting from these compilations at random, the resulting quantum channel becomes a mixture of unitaries \note{cite Debbie Leung}, which has significiantly less coherent error than any single compilation on its own. A simple example of this reduction in coherent error by mixed quantum gates is illustrated in Fig.~\ref{fig:simple_example}. We note that randomized protocols such as theirs have a long history of outperforming their deterministic counterparts. \note{Find some citations - Viola and others - and write a sentence about them, maybe move this to the conclusion? We should also discuss randomized compiling there. }

In this article, we extend the work of Campbell and Hastings to numerically optimized quantum gates, and show that the advantages of this approach can be made robust to drift in the gate implementations. We demonstrate that, depending on the objective, different numerical optimization targets may be preferred. We present an experimental implementation of single-qubit mixed unitary controls on a superconducting qubit testbed at Rigetti Computing. Using randomized benchmarking, we are able to show a marked improvement in error rates, as well as a reduced variance in circuit outcome probabilities, indicating a reduction in the coherence of the error \cite{Ball2016}. We further provide an optimal control approach to the mixed unitary control design problem, and apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.  The resulting convex optimizations can be performed quickly and efficiently. \note{This paragraph is pretty good, but should be cleaned up a bit.}

@@

CPTP maps possesses a number of useful representations, including Kraus operators\cite{1983}, Choi matrices\cite{Choi1975}, and Jamiolkowsi states\cite{yczkowski2004}. But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient\cite{OBrien2004}, and we shall denote the process matrix associated with a given CPTP map $\mathsf{G}$ with the corresponding calligraphic character, $\mathcal{G}$. For a $d$-dimensional quantum state, the process matrix is a $d^2\times d^2$ matrix. A key feature of process matrices is that they are composable and act through the usual matrix multiplication on the vectorized quantum state:
\begin{align}
	\vectorize{\mathsf{\tilde G}(\rho)}
		&= \mathcal{\tilde G}\cdot\vectorize{\rho} \\
		&= \mathcal{E}\cdot\mathcal{G}\cdot\vectorize{\rho}
\end{align}
We shall work in the basis of Pauli matrices, defining $\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}^{\otimes n}$ as the collection of all $4^n$ $n$-qubit Pauli operators (including the identity).  In this basis,
\begin{equation}
  \vectorize{\rho}_i = \tr\!\left(\rho \cdot\Sigma_i\right)/2^n,
\end{equation}
and
\begin{equation}
	(\mathcal{\tilde G})_{ij} = \tr\!\left(\mathsf{\tilde G}\left(\Sigma_j\right) \cdot\Sigma_i\right)/2^n.
\end{equation}
Process matrices written in Pauli basis are is often referred to as \emph{Pauli transfer matrices} \cite{Chow2012}.  Error maps represented this way take the particularly nice form:
\begin{equation}\label{eq:process_matrix}
\mathcal{E} =
	\left(\begin{array}{c|cccc}
		1 &  & \vec{0}^T & \\ 
		\hline & &  &  \\
		\vec{m} &  & R &  \\
		 &  &  & 
	\end{array} 	
	\right)
\end{equation}
The top row of all trace-preserving (TP) error maps is fixed to $\{1,0,0,0,\cdots\}$ and the remainder of the first column, $\vec{m}$, describes any deviations from unitality, as might arise from amplitude damping \note{[]}. If the error map is unitary, then the error is coherent, and the unital submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector. Importantly, if $R$ is diagonal, then the error is Pauli stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate. If $R$ is symmetric but not diagonal, then the channel is stochastic, but the random errors consist of \emph{correlated} Pauli operators (such as $X+Y$). For a single qubit, this rounds out the possibilities, but the situation can be slightly more complicated for more qubits.

@@

\subsection{Mixed Quantum Gates}
\noindent Now suppose that we have access to an ensemble of different implementations of the target gate $\{\mathsf{\tilde G}_i\}$.
% , each associated with a different process matrix, $\mathcal{\tilde G}_i = \mathcal{E}_i\circ \mathcal{G}$. 
Each time the gate is to be applied to the system, we randomly select an implementation from this ensemble such that the probability of drawing $\mathsf{E}_i$ is $w_i$ (and we ensure that $\sum_i w_i=1$). This procedure is operationally indistinguishable from always applying the effective operation, 
\begin{align}
	\mathsf{\tilde G}_{\rm eff} &= \sum_i w_i \mathsf{\tilde G}_i.
\end{align}
We call such randomized quantum operations \emph{mixed quantum gates} or MQGs. Error metrics for MQGs can be computed in terms of their effective error map, 
\begin{equation}
	\label{eq:effective_error}
	\mathsf{E}_{\rm eff} = \sum_i w_i \mathsf{E}_i.
\end{equation}
Two important error metrics are the average gate infidelity (AGI), $\epsilon_\mathcal{F}$, and the diamond distance to the target, $\epsilon_\diamond$ \cite{}, defined as:
\begin{align}
	\label{eq:def_agi}
	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{d^2 - \tr{\mathcal{E}}}{d^2 + d},\\
	\label{eq:def_diamond}
	&\epsilon_\diamond \left(\mathsf{E}\right)
		= \frac{1}{2} \sup_\rho \vert \vert (\mathsf{I}_d\otimes \mathsf{I}_d)(\rho) 
										  - (\mathsf{E} \otimes \mathsf{I}_d)(\rho) \vert\vert_1,
\end{align}
where $d=2^n$ and $\mathsf{I}_d$ is the $d$-dimensional identity operator.  In Eq.~\eqref{eq:def_agi}, we have written the AGI for an error map, $\mathsf{E}$ in terms of its associated Pauli transfer matrix, $\mathcal{E}$. If the error channel is purely stochastic, then $\epsilon_\diamond(\error) = \epsilon_\mathcal{F}(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity \note{[Wallman - Error rates in quantum circuits]}. The diamond distance is subaddative \note{[Watroos TQI book]} under gate composition, so is particularly useful for constructing bounds on quantum circuit performance: the total variation distance between the outcome probabilities of a faulty and perfect quantum circuit is less than or equal to the sum of the diamond distances for the component gates \note{[Aharanov, Kitaev, Nisan, 1998]}.

@@

Campbell \cite{Campbell2017} and Hastings \cite{1612.01011} independently considered this problem using gates constructed with the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible. Campbell showed that, if the error generators of some ensemble of gate compilations form a convex set containing the origin, then one can construct a mixed quantum gate with quadratically suppressed diamond distance to the target. Explicitly, the weight are chosen such that the error generator is canceled to first order. Using Eqs.~\eqref{eq:effective_error} and \eqref{eq:generator}, the effective error map for a mixed quantum gate in terms of the component error generators is:
\begin{align}
	\label{eq:generators_and_effective_error}
	\mathcal{E}_{\rm eff} \simeq \left(\mathcal{I}_d + \sum_i w_i \mathcal{L}_i + \frac{1}{2} \sum_i w_i \mathcal{L}_i^2\right)
\end{align}
If, as Campbell required, the origin is in the convex hull of the generators (see Fig.~\ref{fig:vectorspace}), then there exists a choice for the weights, $w_i^*$, such that $\sum_i w^*=1$ and:
\begin{align}
	\label{eq:cancel}
	&\sum_i w_i^* \mathcal{L} = 0
	% \mathrm{with}\;&\sum_i w_i = 1
\end{align}
If the error rates of the component gates are bounded by $\alpha$, then Campbell shows that this first-order cancellation of the error generators can ensure that the error rate of the MQG is bounded by $\alpha^2$. Campbell considered error channels that were strictly unitary, so the error generators in Eq.~\ref{eq:cancel} were Hamiltonians. Hamiltonian generators can have positive or negative coefficients, so it is possible that the origin may lie in their convex hull. If, however, the error map contains stochastic components, then the condition of Eq.~\ref{eq:cancel} might be impossible to satisfy. Such errors always have positive probabilities, so the origin can \emph{never} lie in their convex hull. This can be rectified by restricting the sum in Eq.~\eqref{eq:cancel} to only the Hamiltonian component of the generators. In the rest of this paper, we will be considering gates that have only unitary errors, so we will neglect this complication going forward.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{vectorspace.pdf}
  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error. These error Hamiltonians lie in a vector space. a) Four effective Hamiltonians. The origin is not contained in their convex hull, so there are no 0MQCs. b) The origin is contained in the covex hull after adding an additional control solution. Because there are more than $n+1$ implementations, there exist an infinite number of 0MQCs. c) The error Hamiltonians shown with their derivative with respect to a control parameter. As this parameter drifts, a 0MQC may drift, leading to a first-order error. d) The derivatives also lie in a vector space. If the origin lies in their convex hull, then it may be possible to construct a 1MQC.}
  \label{fig:vectorspace}
\end{figure}

@@

\begin{equation}
	\mathcal{E}_{\rm{eff}} = 
	\left(\begin{array}{@{}ccccc@{}}
		1 & 0 & 0 & 0 \\ 
    	0 &  p_x & 0 & 0 \\
		0 & 0 &  p_y & 0\\
		0 & 0 & 0 &  p_z\\
	\end{array} 	
	\right).
\end{equation}
The resulting mixed quantum gate is then guaranteed to have a Pauli stochastic error channel, and significantly increasing its simulability. We can formulate this problem in analogously to the generator approach. The off-diagonal elements of the error map form a vector space, so to ensure that such a solution is possible, we need only check that the origin is in the convex hull of the vectors of off-diagonal elements for each of the component operations, $\mathcal{E}_i$.

@@

% ==============================================================================
% Section: Constructing Useful mixed quantum gates
% ==============================================================================
\section{Constructing mixed quantum gates}
\label{sec:mixed_unitary_processes}
\noindent In this section, we present a methodology for producing useful mixed quantum channels, formalizing the intuitive approach discussed above. As mentioned, our method requires two steps. The first is a control synthesis step, in which we construct an ensemble of gate implementations. Campbell and Hastings draw their ensembles from various different gate compilations, but for this work, we use quantum optimal control theory to produce these ensembles. By running simple gradient descent algorithms, such as GRAPE \cite{Khaneja2005}, with different random initial seeds, one can quickly construct large ensembles of approximate quantum gates. We discuss this approach in some detail in Sec.~\ref{sec:numerical_results}. We note that advanced quantum control protocols may provide a more principled approach to control synthesis. DMORPH [Rabiz and Dominey], for example, allows one to explore families of controls on fidelity level sets.

@@

% In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin in some high-dimensional vector space. In those cases, the vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps. As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivatives of the error generators to minimize the sensitivity of the controls to drift. In this way, we see that by considering the appropriate collection of vectors, we can optimize our MQC for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.

@@

If our primary goal is for our MQC to have increased worst-case performance, then a useful target for constructing MQCs is to minimize the diamond norm. The diamond norm is a non-linear function that in general requires a convex optimizer to compute. However, if our errors are small enough, we can consider the linearized problem, and minimize the diamond norm to first-order in the error generator. As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of an MQC with error generators $\{G_j\}$ to first order is:
\begin{equation}\label{eq:campbell-condition}
\sum \omega_j G_j = 0
\end{equation}
In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, generates controls and weightings to find an MQC with this property. Alternatively one might ask the question: \textit{Given a fixed collection of controls, how can I produce a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we randomly generate a collection of gate implementations. In these situations, one can use convex optimization to solve this problem. Given a collection of controls in our MQC, each will have an associated error channel $\error_i$ given by $\error_i\actual_i=\target$. We can then consider the matrix whose columns are the vectorized generators of the error channels for each control, i.e. $G_i$ such that $e^{G_i}=\error_i$. Then we will have $m$, $n\times n$ generators:
\begin{equation}\label{eq:vectorized_generators}
	\bold{G} = \left(\begin{array}{cccc}
		G_{1_{1,1}} & G_{2_{1,1}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		G_{1_{n,n}} &  &  G_{m_{n,n}} \\ 
	\end{array} 	
	\right)
\end{equation}
If our weighting vector for our MQC is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero. Additionally, this optimization needs to be constrained so that $\omega \geq 0$ and $|\omega|_1 = 1$. This forms a convex optimization problem, and can be written as:

\begin{equation}\label{eq:minimization}
  \begin{split}
    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||\bold{G}\omega||_2\\
  \end{split}
\end{equation}

@@

%Another interesting property of the MQC given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift. In particular, if the control amplitudes that implement these gates drift, they will drift in equal and opposite ways. Thus, the resulting depolarizing channel (see Figure \ref{fig:simple_example}) will have a time-dependent strength, but it will remain first-order insensitivity to the static detuning $\epsilon$. In Section \ref{sec:robustly_mixed} we will provide a method for producing controls that exhibit this robustness to drift to arbitrary order. Given these considerations from this simple example, we will now consider a numerical strategy for generating MQCs.

@@

\subsubsection{Off-diagonals} % (fold)
\label{sub:off_diagonals}
Of course, there are other properties of a channel that one might consider optimizing. Instead of minimizing the diamond norm, we might want our resulting MQC to have an error channel that is well-approximated by a Pauli-Stochastic channel, so that the error on our channel is amenable to classical simulation. We can write this error channel as a process matrix, vectorize the $R$ submatrices in Equation \ref{eq:process_matrix}, and consider the matrix of off-diagonal terms:

\begin{equation}\label{eq:vectorized_off_diagonal}
	\bold{R} = \left(\begin{array}{cccc}
		R_{1_{2,1}} & R_{2_{2,1}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		R_{1_{n-1,n-1}} &  &  R_{m_{n-1,n-1}} \\ 
	\end{array} 	
	\right)
\end{equation}
then again we consider the same minimization problem, where we replace $\bold{G}$ with $\bold{R}$:

@@

Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, however this requires multiple evaluations of the diamond norm, and in particular does not have the restriction that the resulting channel be decomposable into a given family of controls. Our approach, on the other hand, guarantees that the resulting MQC is able to be implemented with the available controls, and is an easy-to-solve quadratic program. \note{what does this mean?}
% subsection off_diagonals (end)

>>>>

\begin{abstract}
\noindent Coherent errors in quantum operations are ubiquitous. Whether arising from spurious environmental couplings or errors in control fields, such errors can accumulate rapidly and degrade the performance of a quantum circuit significantly more than an average gate fidelity may indicate. As Hastings \cite{Hastings2017} and Campbell \cite{Campbell2017} have recently shown, randomly sampling an ensemble of implementations of a target gate yields an effective quantum channel that well-approximates the target, but with dramatically suppressed coherent error. Our work begins by reformulating the results of Hastings and Campbell as a quantum optimal control problem. We then discuss a family of convex programs designed to improve the performance, implementability, and robustness of the resulting mixed quantum gates. Finally, we implement these mixed quantum gates on a superconducting qubit and discuss randomized benchmarking results consistent with a marked reduction in the coherent error.\\
{[1]} M. B. Hastings, \emph{Quantum Information \& Computation} 17, 488 (2017). \\
{[2]} E. Campbell, \emph{Physical Review A} 95, 042306 (2017).
\end{abstract}

@@

% ==============================================================================
% Section: Introduction
% ==============================================================================
\section{Introduction}
\label{sec:introduction}
\noindent The ultimate impact of a gate error on a quantum circuit depends strongly on both the magnitude and the nature of the error. Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or approximate gate compilations that induce repeatable, undesired unitary errors on the state of a QIP. Errors of this type are correlated in time may add up constructively or destructively, depending on the circuit. They are are  computationally expensive to model and, because coherent errors may amplify when gates are repeated, it can be difficult to place tight analytic bounds on circuit performance \cite{Beale2018}. Contrast this against random, or \emph{stochastic}, errors, which often result from high-frequency noise in the controls or the environment. Systems with stochastic errors can usually be accurately modeled by defining a rate of various discrete errors in the system, such as a bit flips or phase flips. These errors are significantly easier to simulate on a classical computer, and their impact on quantum circuits is much easier to estimate \cite{Beale2018}.

@@

Recent works by Campbell \cite{Campbell2017,1811.08017} and Hastings \cite{Hastings2017} have shown that coherent noise can be strongly suppressed by probabilistically mixing several distinct implementations of the target quantum gates. They focus on errors arising from various gate compilations, such as the Solovey-Kitaev algorithm, for which any lingering approximation errors are generally coherent, even if the native gates are perfect. Different approximate gate compilations of the same target unitary will almost certainly result in a different unitary error. So by selecting from these compilations at random, the resulting quantum channel becomes a mixture of unitaries \cite{DBLP:journals/corr/cs-CC-0012017}, which has significantly less coherent error than any single compilation on its own. A simple example of this reduction in coherent error by mixed quantum gates is illustrated in Fig.~\ref{fig:simple_example}.

In this article, we extend the work of Campbell and Hastings to numerically optimized quantum gates, and show that the advantages of this approach can be made robust to drift in the gate implementations. We demonstrate that, depending on what properties of the resulting channel are desired, different numerical optimization targets may be preferred. We present an experimental implementation of single-qubit mixed unitary controls on a superconducting qubit testbed at Rigetti Computing. Using randomized benchmarking, we are able to show a marked improvement in error rates, as well as a reduced variance in circuit outcome probabilities, indicating a reduction in the coherence of the error \cite{Ball2016}. We further provide an optimal control approach to the mixed unitary control design problem, and apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.

@@

CPTP maps possess a number of useful representations, including Kraus operators\cite{1983}, Choi matrices\cite{Choi1975}, and Jamiolkowsi states\cite{yczkowski2004}. But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient\cite{OBrien2004}, and we shall denote the process matrix associated with a given CPTP map $\mathsf{G}$ with the corresponding calligraphic character, $\mathcal{G}$. For a $d$-dimensional quantum state, the process matrix is a $d^2\times d^2$ matrix. A key feature of process matrices is that they are composable and act through the usual matrix multiplication on the vectorized quantum state:
\begin{align}
	\vectorize{\mathsf{\tilde G}(\rho)}
		&= \mathcal{\tilde G}\cdot\vectorize{\rho} \\
		&= \mathcal{E}\cdot\mathcal{G}\cdot\vectorize{\rho}
\end{align}
We shall work in the basis of Pauli matrices, defining $\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}^{\otimes n}$ as the collection of all $4^n$ $n$-qubit Pauli operators (including the identity).  In this basis,
\begin{equation}
  \vectorize{\rho}_i = \tr\!\left(\rho \cdot\Sigma_i\right)/2^n,
\end{equation}
and
\begin{equation}
	(\mathcal{\tilde G})_{ij} = \tr\!\left(\mathsf{\tilde G}\left(\Sigma_j\right) \cdot\Sigma_i\right)/2^n.
\end{equation}
Process matrices written in the Pauli basis are often referred to as \emph{Pauli transfer matrices} \cite{Chow2012}.  Error maps represented this way take the particularly nice form:
\begin{equation}\label{eq:process_matrix}
\mathcal{E} =
	\left(\begin{array}{c|cccc}
		1 &  & \vec{0}^T & \\ 
		\hline & &  &  \\
		\vec{m} &  & R &  \\
		 &  &  & 
	\end{array} 	
	\right)
\end{equation}
The top row of all trace-preserving (TP) error maps is fixed to $\{1,0,0,0,\cdots\}$ and the remainder of the first column, $\vec{m}$, describes any deviations from unitality, as might arise from amplitude damping \note{[]}. If the error map is unitary, then the error is called \textit{coherent} , and the unital submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector. Importantly, if $R$ is diagonal, then the error is Pauli stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate. If $R$ is symmetric but not diagonal, then the channel is stochastic, but the random errors consist of \emph{correlated} Pauli operators (such as $X+Y$). For a single qubit, this rounds out the possibilities, but the situation can be slightly more complicated for more qubits.

@@

\subsection{Mixed Quantum Gates}
\noindent Now suppose that we have access to an ensemble of different implementations of the target gate, $\{\mathsf{\tilde G}_i\}$.
% , each associated with a different process matrix, $\mathcal{\tilde G}_i = \mathcal{E}_i\circ \mathcal{G}$. 
Each time the gate is to be applied to the system, we randomly select an implementation from this ensemble such that the probability of drawing $\mathsf{\tilde{G}}_i$ is $w_i$ (and we ensure that $\sum_i w_i=1$). This procedure is operationally indistinguishable from always applying the effective operation, 
\begin{align}
	\mathsf{\tilde G}_{\rm eff} &= \sum_i w_i \mathsf{\tilde G}_i.
\end{align}
We call such randomized quantum operations \emph{mixed quantum gates} or MQGs. Error metrics for MQGs can be computed in terms of their effective error map, 
\begin{equation}
	\label{eq:effective_error}
	\mathsf{E}_{\rm eff} = \sum_i w_i \mathsf{E}_i.
\end{equation}
Two important error metrics are the average gate infidelity (AGI), $\epsilon_\mathcal{F}$, and the diamond distance to the target, $\epsilon_\diamond$ \cite{}, defined as:
\begin{align}
	\label{eq:def_agi}
	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{d^2 - \tr{\mathsf{E}}}{d^2 + d},\\
	\label{eq:def_diamond}
	&\epsilon_\diamond \left(\mathsf{E}\right)
		= \frac{1}{2} \sup_\rho \vert \vert (\mathsf{I}_d\otimes \mathsf{I}_d)(\rho) 
										  - (\mathsf{E} \otimes \mathsf{I}_d)(\rho) \vert\vert_1,
\end{align}
where $d=2^n$ and $\mathsf{I}_d$ is the $d$-dimensional identity operator.  In Eq.~\eqref{eq:def_agi}, we have written the AGI for an error map, $\mathsf{E}$, in terms of its associated Pauli transfer matrix, $\mathcal{E}$. If the error channel is purely stochastic, then $\epsilon_\diamond(\error) = \epsilon_\mathcal{F}(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity \cite{1511.00727}. The diamond distance is subaddative \cite{watrous2018theory} under gate composition, so is particularly useful for constructing bounds on quantum circuit performance: the total variation distance between the outcome probabilities of a faulty and perfect quantum circuit is less than or equal to the sum of the diamond distances for the component gates \cite{aharonov1998quantum}.

@@

Campbell \cite{Campbell2017} and Hastings \cite{1612.01011} independently considered this problem using gates constructed with the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible. Campbell showed that, if the error generators of some ensemble of gate compilations form a convex set containing the origin, then one can construct a mixed quantum gate with quadratically suppressed diamond distance to the target. Explicitly, the weights are chosen such that the error generator is canceled to first order. Using Eqs.~\eqref{eq:effective_error} and \eqref{eq:generator}, the effective error map for a mixed quantum gate in terms of the component error generators is:
\begin{align}
	\label{eq:generators_and_effective_error}
	\mathcal{E}_{\rm eff} \simeq \left(\mathcal{I}_d + \sum_i w_i \mathcal{L}_i + \frac{1}{2} \sum_i w_i \mathcal{L}_i^2\right)
\end{align}
If, as Campbell required, the origin is in the convex hull of the generators (see Fig.~\ref{fig:vectorspace}), then there exists a choice for the weights, $w_i^*$, such that $\sum_i w^*=1$ and:
\begin{align}
	\label{eq:cancel}
	&\sum_i w_i^* \mathcal{L} = 0
	% \mathrm{with}\;&\sum_i w_i = 1
\end{align}
If the error rates, as measured by the diamond distance, of the component gates are bounded by $\alpha$, then Campbell shows that this first-order cancellation of the error generators can ensure that the error rate of the MQG is bounded by $\alpha^2$. Campbell considered error channels that were strictly unitary, so the error generators in Eq.~\ref{eq:cancel} were Hamiltonians. Hamiltonian generators can have positive or negative coefficients, so it is possible that the origin may lie in their convex hull. If, however, the error map contains stochastic components, then the condition of Eq.~\ref{eq:cancel} might be impossible to satisfy. Such errors always have positive probabilities, so the origin can \emph{never} lie in their convex hull. This can be rectified by restricting the sum in Eq.~\eqref{eq:cancel} to only the Hamiltonian component of the generators. In the rest of this paper, we will be considering gates that have only unitary errors, so we will neglect this complication going forward.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{vectorspace.pdf}
  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error. These error Hamiltonians lie in a vector space. a) Four effective Hamiltonians. The origin is not contained in their convex hull, so there are no 0MQGs. b) The origin is contained in the covex hull after adding an additional control solution. Because there are more than $n+1$ implementations, there exist an infinite number of 0MQGs. c) The error Hamiltonians shown with their derivative with respect to a control parameter. As this parameter drifts, a 0MQG may drift, leading to a first-order error. d) The derivatives also lie in a vector space. If the origin lies in their convex hull, then it may be possible to construct a 1MQG.}
  \label{fig:vectorspace}
\end{figure}

@@

\begin{equation}
	\mathcal{E}_{\rm{eff}} = 
	\left(\begin{array}{@{}ccccc@{}}
		1 & 0 & 0 & 0 \\ 
    	0 &  p_x & 0 & 0 \\
		0 & 0 &  p_y & 0\\
		0 & 0 & 0 &  p_z\\
	\end{array} 	
	\right).
\end{equation}
The resulting mixed quantum gate is then guaranteed to have a Pauli stochastic error channel, and significantly increasing its simulability. We can formulate this problem analogously to the generator approach. The off-diagonal elements of the error map form a vector space, so to ensure that such a solution is possible, we need only check that the origin is in the convex hull of the vectors of off-diagonal elements for each of the component operations, $\mathcal{E}_i$.

@@

% ==============================================================================
% Section: Constructing Useful mixed quantum gates
% ==============================================================================
\section{Constructing mixed quantum gates}
\label{sec:mixed_unitary_processes}
\noindent In this section, we present a methodology for producing useful mixed quantum channels, formalizing the intuitive approach discussed above. As mentioned, our method requires two steps. The first is a control synthesis step, in which we construct an ensemble of gate implementations. Campbell and Hastings draw their ensembles from various different gate compilations, but for this work we use quantum optimal control theory to produce these ensembles. By running simple gradient descent algorithms, such as GRAPE \cite{Khaneja2005}, with different random initial seeds, one can quickly construct large ensembles of approximate quantum gates. We discuss this approach in some detail in Sec.~\ref{sec:numerical_results}. We note that advanced quantum control protocols may provide a more principled approach to control synthesis. DMORPH \cite{dominy2008exploring}, for example, allows one to explore families of controls on fidelity level sets.

@@

% In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin in some high-dimensional vector space. In those cases, the vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps. As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivatives of the error generators to minimize the sensitivity of the controls to drift. In this way, we see that by considering the appropriate collection of vectors, we can optimize our MQG for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.

@@

If our primary goal is for our MQG to have increased worst-case performance, then a useful target for constructing MQGs is to minimize the diamond norm. The diamond norm is a non-linear function that in general requires a convex optimizer to compute. However, if our errors are small enough, we can consider the linearized problem, and minimize the diamond norm to first-order in the error generator. As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of an MQG with error generators $\{G_j\}$ to first order is:
\begin{equation}\label{eq:campbell-condition}
\sum \omega_j G_j = 0
\end{equation}
In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, generates controls and weightings to find an MQG with this property. Alternatively one might ask the question: \textit{Given a fixed collection of controls, how can I produce a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we randomly generate a collection of gate implementations. In these situations, one can use convex optimization to solve this problem. Given a collection of controls in our MQG, we can consider the $n^2\times m$ matrix whose columns are the vectorized error generators:
\begin{equation}\label{eq:vectorized_generators}
	\bold{H} = \left(\begin{array}{cccc}
		H_{1_{1,1}} & H_{2_{1,1}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		H_{1_{n,n}} &  &  H_{m_{n,n}} \\ 
	\end{array} 	
	\right)
\end{equation}
If our weighting vector for our MQG is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero. Additionally, this optimization needs to be constrained so that $\omega \geq 0$ and $|\omega|_1 = 1$. This forms a convex optimization problem, and can be written as:

\begin{equation}\label{eq:minimization}
  \begin{split}
    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||\bold{H}\omega||_2\\
  \end{split}
\end{equation}

@@

%Another interesting property of the MQG given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift. In particular, if the control amplitudes that implement these gates drift, they will drift in equal and opposite ways. Thus, the resulting depolarizing channel (see Figure \ref{fig:simple_example}) will have a time-dependent strength, but it will remain first-order insensitivity to the static detuning $\epsilon$. In Section \ref{sec:robustly_mixed} we will provide a method for producing controls that exhibit this robustness to drift to arbitrary order. Given these considerations from this simple example, we will now consider a numerical strategy for generating MQGs.

@@

\subsubsection{Off-diagonals} % (fold)
\label{sub:off_diagonals}
Of course, there are other properties of a channel that one might consider optimizing. Instead of minimizing the diamond norm, we might want our resulting MQG to have an error channel that is well-approximated by a Pauli-Stochastic channel, so that the error on our channel is amenable to classical simulation. We can write this error channel as a process matrix, vectorize the $R$ submatrices in Equation \ref{eq:process_matrix}, and consider the matrix of off-diagonal terms:

\begin{equation}\label{eq:vectorized_off_diagonal}
	\bold{R} = \left(\begin{array}{cccc}
		R_{1_{2,1}} & R_{2_{2,1}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		R_{1_{n-1,n-1}} &  &  R_{m_{n-1,n-1}} \\ 
	\end{array} 	
	\right)
\end{equation}
then again we consider the same minimization problem, where we replace $\bold{H}$ with $\bold{R}$:

@@

Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, however this requires multiple evaluations of the diamond norm, and in particular does not have the restriction that the resulting channel be decomposable into a given family of controls. Our approach, on the other hand, guarantees that the resulting MQG is able to be implemented with the available controls, and is an easy-to-solve quadratic program. \note{what does this mean?}
% subsection off_diagonals (end)
